### 2017-10-14 Gruba/07-rela.tex

With respect to feature analysis, there have been existing work of mining user features, such as race \cite{IEEEexample:conf/icwsm/PennacchiottiP11}, gender \cite{IEEEexample:conf/emnlp/CiotSR13}, age \cite{IEEEexample:conf/icde/ParkHHL09}, political preference \cite{IEEEexample:conf/icwsm/PennacchiottiP11,IEEEexample:conf/acl/VolkovaCD14,IEEEexample:kosinski2013private} and occupation \cite{IEEEexample:journals/tmm/FangSXH15,IEEEexample:conf/icde/FanCTWC16}.
Our work, however, does not focus on the mining process per se; we use the mined features as the input for user clustering and group based behavior modeling.

>>>>

For feature analysis, there has been existing work of mining user features, such as race \cite{IEEEexample:conf/icwsm/PennacchiottiP11}, gender \cite{IEEEexample:conf/emnlp/CiotSR13}, age \cite{IEEEexample:conf/icde/ParkHHL09}, political preference \cite{IEEEexample:conf/icwsm/PennacchiottiP11,IEEEexample:conf/acl/VolkovaCD14,IEEEexample:kosinski2013private} and occupation \cite{IEEEexample:journals/tmm/FangSXH15,IEEEexample:conf/icde/FanCTWC16}.
Our work, however, does not focus on the mining process, but uses the mined features as the input for user clustering and group based behavior modeling.
